### 2022-05-30 manuscript/manuscript.Rmd
use PRC not PPPR abbreviation

PPPR_category_plotter <- function(d){
   ggplot(d, aes(y = PPPR_category, x = n, label = ifelse(var_type == "Any PPPR",paste0(round((n/15)*100,0),'%'),''), colour = var_type)) +
    geom_segment(aes(x=0, xend=n, y=PPPR_category, yend=PPPR_category)) +
    geom_point(aes(size = var_type)) +
    geom_text(color="black", size = 2.5) +
    scale_colour_manual(values = c(purple, green), guide = 'none') +
    scale_size_manual(values = c(8,2), guide = 'none') +
    scale_x_continuous(limits = c(0,17), breaks = seq(0,15,5)) +
    xlab(expression(paste('journals (',italic('n'),')'))) +
    ggtitle(str_wrap(d$field, 18)) +
    theme(
      panel.grid.major.y = element_blank(),
      axis.title.y = element_blank(),
      axis.title.x = element_blank(),
      plot.title = element_text(size = 7))
}

PPPR_category_plotter_allFields <- function(d){
   ggplot(d, aes(y = PPPR_category, x = n, label = 
     ifelse(var_type == "Any PPPR",paste0(round((n/330)*100,0),'%'),''), 
     colour = var_type)) +
    geom_segment(aes(x=0, xend=n, y=PPPR_category, yend=PPPR_category)) +
    geom_point(aes(size = var_type)) +
    geom_text(color="black", size = 2.5) +
    scale_colour_manual(values = c(purple, green), guide = 'none') +
    scale_size_manual(values = c(8,2), guide = 'none') +
    scale_x_continuous(limits = c(0,225), breaks = seq(0,225,25)) +
    ggtitle(d$field) +
    theme(
      panel.grid.major.y = element_blank(),
      axis.title.y = element_blank(),
      axis.title.x = element_blank(),
      plot.title = element_text(size = 7))
}

thisData <- d_policy %>% 
  filter(!is.na(PPPR_name)) %>% 
  mutate(PPPR_category = factor(PPPR_name_harmonized)) %>%
  count(PPPR_category, field, .drop = F) %>%
  bind_rows(
    d_policy %>%
      filter(PPPR_type == 'A') %>% # only need the first entry for each journal
      count(field, anyPPPR) %>%
      filter(anyPPPR == T) %>%
      select(-anyPPPR) %>%
      mutate(PPPR_category = 'Any PPPR')
  ) %>%
  mutate(PPPR_category = factor(PPPR_category, levels = c("Other", "Web comments", "Commentaries", "Letters", "Any PPPR")),
         var_type = ifelse(PPPR_category == "Any PPPR", "Any PPPR", "Other"),
         field = factor(field, levels = rev(levels(policySummary$field)[2:23]))) # reorder levels by proportion offering any PPPR

@@

# define function to make limit category plot (lollipop plot for all data)
limitCategoriesPlot <- function(d, thisTitle){
    d %>% 
      mutate(
        limits = case_when(
          limits %notin% c('Qualitative limit','NOT STATED', 'NO') ~ 'Quant', # classify all numeric length limits under same category
          limits == 'Qualitative limit' ~ 'Qual',
          limits == 'NOT STATED' ~ 'Not stated',
          limits == 'NO' ~ 'None',
          TRUE ~ NA_character_
          ),
        limits = factor(limits, levels = c('Quant', 'Qual', 'None', 'Not stated')),
        type = ifelse(limits == 'Quant', 'Quant', 'Other') # this is used to have a different colour for numeric limit data
        ) %>% 
    count(limits, type) %>%
    ggplot(aes(x = limits, y = n, label = n, fill = type)) +
    geom_col(colour = 'grey10') +
    geom_text(aes(y = n + 18), color="black", size = 3) +
    ylab(expression(paste('PPPRs (',italic('n'),')'))) +
    scale_y_continuous(expand = c(0, 0), limits = c(0,200), breaks = seq(0,200,100)) +
    scale_fill_manual(values = c(nonnumericColour,numericColour), guide = 'none') +
    theme(axis.title.y = element_text(size = 10),
          axis.title.x = element_blank(),
          axis.line = element_line(colour = 'grey10'),
          axis.ticks = element_line(colour = 'grey10'),
          panel.grid = element_blank(),
          plot.title = element_text(size = 11))
}

# define function to make limit numeric plot (histogram + box plot)
limitNumericPlot <- function(d, thisBinWidth, thisBoxWidth){
  d %>% 
    filter(limits %notin% c('Qualitative limit','NOT STATED', 'NO')) %>%
    mutate(limits = as.numeric(limits)) %>%
    ggplot(aes(x = limits)) +
    geom_histogram(
      #aes(fill = PPPR_name_harmonized), 
      position = position_stack(reverse = TRUE),
      alpha = .65,
      binwidth = thisBinWidth,
      colour = 'grey10') +
    geom_boxplot(
      aes(y = -thisBoxWidth),
      fill = NA,
      width = thisBoxWidth,
      outlier.shape = NA,
      alpha = 1,
      colour = 'grey10') +
    expand_limits(x = 0) +
    ylab('PPPRs (n)') +
    theme(
      axis.line = element_blank(),
      axis.ticks = element_line(colour = 'grey10'),
      panel.grid.major.y = element_blank())
}
```

@@

>>>>

PPPR_category_plotter <- function(d){
   ggplot(d, aes(y = PPPR_category, x = n, label = ifelse(var_type == "Any PPC",paste0(round((n/15)*100,0),'%'),''), colour = var_type)) +
    geom_segment(aes(x=0, xend=n, y=PPPR_category, yend=PPPR_category)) +
    geom_point(aes(size = var_type)) +
    geom_text(color="black", size = 2.5) +
    scale_colour_manual(values = c(purple, green), guide = 'none') +
    scale_size_manual(values = c(8,2), guide = 'none') +
    scale_x_continuous(limits = c(0,17), breaks = seq(0,15,5)) +
    xlab(expression(paste('journals (',italic('n'),')'))) +
    ggtitle(str_wrap(d$field, 18)) +
    theme(
      panel.grid.major.y = element_blank(),
      axis.title.y = element_blank(),
      axis.title.x = element_blank(),
      plot.title = element_text(size = 7))
}

PPPR_category_plotter_allFields <- function(d){
   ggplot(d, aes(y = PPPR_category, x = n, label = 
     ifelse(var_type == "Any PPC",paste0(round((n/330)*100,0),'%'),''), 
     colour = var_type)) +
    geom_segment(aes(x=0, xend=n, y=PPPR_category, yend=PPPR_category)) +
    geom_point(aes(size = var_type)) +
    geom_text(color="black", size = 2.5) +
    scale_colour_manual(values = c(purple, green), guide = 'none') +
    scale_size_manual(values = c(8,2), guide = 'none') +
    scale_x_continuous(limits = c(0,225), breaks = seq(0,225,25)) +
    ggtitle(d$field) +
    theme(
      panel.grid.major.y = element_blank(),
      axis.title.y = element_blank(),
      axis.title.x = element_blank(),
      plot.title = element_text(size = 7))
}

thisData <- d_policy %>% 
  filter(!is.na(PPPR_name)) %>% 
  mutate(PPPR_category = factor(PPPR_name_harmonized)) %>%
  count(PPPR_category, field, .drop = F) %>%
  bind_rows(
    d_policy %>%
      filter(PPPR_type == 'A') %>% # only need the first entry for each journal
      count(field, anyPPPR) %>%
      filter(anyPPPR == T) %>%
      select(-anyPPPR) %>%
      mutate(PPPR_category = 'Any PPPR')
  ) %>%
  mutate(
    PPPR_category= ifelse(PPPR_category == "Any PPPR", "Any PPC", PPPR_category),
    PPPR_category = factor(PPPR_category, levels = c("Other", "Web comments", "Commentaries", "Letters", "Any PPC")),
    var_type = ifelse(PPPR_category == "Any PPC", "Any PPC", "Other"),
    field = factor(field, levels = rev(levels(policySummary$field)[2:23]))) # reorder levels by proportion offering any PPPR

@@

# define function to make limit category plot (lollipop plot for all data)
limitCategoriesPlot <- function(d, thisTitle){
    d %>% 
      mutate(
        limits = case_when(
          limits %notin% c('Qualitative limit','NOT STATED', 'NO') ~ 'Quant', # classify all numeric length limits under same category
          limits == 'Qualitative limit' ~ 'Qual',
          limits == 'NOT STATED' ~ 'Not stated',
          limits == 'NO' ~ 'None',
          TRUE ~ NA_character_
          ),
        limits = factor(limits, levels = c('Quant', 'Qual', 'None', 'Not stated')),
        type = ifelse(limits == 'Quant', 'Quant', 'Other') # this is used to have a different colour for numeric limit data
        ) %>% 
    count(limits, type) %>%
    ggplot(aes(x = limits, y = n, label = n, fill = type)) +
    geom_col(colour = 'grey10') +
    geom_text(aes(y = n + 18), color="black", size = 3) +
    ylab(expression(paste('PPCs (',italic('n'),')'))) +
    scale_y_continuous(expand = c(0, 0), limits = c(0,200), breaks = seq(0,200,100)) +
    scale_fill_manual(values = c(nonnumericColour,numericColour), guide = 'none') +
    theme(axis.title.y = element_text(size = 10),
          axis.title.x = element_blank(),
          axis.line = element_line(colour = 'grey10'),
          axis.ticks = element_line(colour = 'grey10'),
          panel.grid = element_blank(),
          plot.title = element_text(size = 11))
}

# define function to make limit numeric plot (histogram + box plot)
limitNumericPlot <- function(d, thisBinWidth, thisBoxWidth){
  d %>% 
    filter(limits %notin% c('Qualitative limit','NOT STATED', 'NO')) %>%
    mutate(limits = as.numeric(limits)) %>%
    ggplot(aes(x = limits)) +
    geom_histogram(
      #aes(fill = PPPR_name_harmonized), 
      position = position_stack(reverse = TRUE),
      alpha = .65,
      binwidth = thisBinWidth,
      colour = 'grey10') +
    geom_boxplot(
      aes(y = -thisBoxWidth),
      fill = NA,
      width = thisBoxWidth,
      outlier.shape = NA,
      alpha = 1,
      colour = 'grey10') +
    expand_limits(x = 0) +
    ylab('PPCs (n)') +
    theme(
      axis.line = element_blank(),
      axis.ticks = element_line(colour = 'grey10'),
      panel.grid.major.y = element_blank())
}
```

@@

# (APPENDIX) Appendix {-}

```{r child = "supplementary_information.Rmd"}
```
